Bad forecast, good decision: predictive accuracy is not everything

### 2020-12-04 manuscript/manuscript.Rmd
reformatting

---
title: 'Bad forecast, good decision: predictive accuracy is not everything'
author:
- name: Carl Boettiger
  email: cboettig@berkeley.edu
  affiliation: ucb
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
abstract: |
  Model-based forecasts have been enabled by recent explosion of data and computational methods and spurred on by decision-makers appetite for forecasts in everything from elections to pandemic response. It is taken for granted that the model which makes the most accurate forecast, accounting for uncertainty, will also be the best model to inform decision-making.  Using a classic example from fisheries management, I demonstrate that selecting the model that produces the best forecast can lead to decidedly worse outcomes. This situation can arise whenever the models are only approximations of the reality, underscoring the risk of evaluating models only by prediction accuracy and not decision outcomes
journal: ' '
layout: 3p
bibliography: refs.bib
csl: science.csl
address:
- code: ucb
  address: ESPM Department, University of California, 130 Mulford Hall Berkeley, CA
    94720-3114, USA
keywords:
- transients,
- optimal control,
- adaptive management,
- stochasticity,
- uncertainty,
- ecological management
preamble: |
  \journal{preprint}
  \usepackage{lineno}
  \linenumbers
---

@@

# Acknowledgements

This work was supported in part by NSF CAREER (#1942280) and computational resources from NSF's XSEDE Jetstream (DEB160003) and Chameleon cloud platforms.

>>>>

---
title: 'Bad forecast, good decision: predictive accuracy is not everything'
author:
- name: Carl Boettiger
  email: cboettig@berkeley.edu
  affiliation: ucb,corr
date: "`r Sys.Date()`"
output: rticles::pnas_article
abstract: |
  Model-based forecasts have been enabled by recent explosion of data and computational methods and spurred on by decision-makers appetite for forecasts in everything from elections to pandemic response. It is taken for granted that the model which makes the most accurate forecast, accounting for uncertainty, will also be the best model to inform decision-making.  Using a classic example from fisheries management, I demonstrate that selecting the model that produces the best forecast can lead to decidedly worse outcomes. This situation can arise whenever the models are only approximations of the reality, underscoring the risk of evaluating models only by prediction accuracy and not decision objectives using formal tools of decision theory.

corresponding_author:
  code: corr
  text: "To whom correspondence should be addressed. E-mail: cboettig@berkeley.edu"

bibliography: refs.bib
address:
- code: ucb
  address: ESPM Department, University of California, 130 Mulford Hall Berkeley, CA
    94720-3114, USA

keywords:
- transients,
- optimal control,
- adaptive management,
- stochasticity,
- uncertainty,
- ecological management

# For footer text
lead_author_surname: Boettiger

significance: |
  ...

acknowledgements: |
  This work was supported in part by NSF CAREER (#1942280) and computational resources from NSF's XSEDE Jetstream (DEB160003) and Chameleon cloud platforms.

keywords:
  - one
  - two
  - optional
  - optional
  - optional

## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
pnas_type: pnasresearcharticle
csl: pnas.csl

## change to true to add optional line numbering
lineno: true

output: rticles::pnas_article

---

@@
